First steps towards a formalization of Forcing

### 2018-07-13 LSFA/arXiv/first_steps_into_forcing.tex
typo

\documentclass{article}
\usepackage{isabelle,isabellesym}
\usepackage{hyperref}

@@

  Given a transitive set $M$, we define its generic extension $M[G]$,
  the canonical names for elements of $M$, and finally show that if $M$
  satisfy the axiom of pairing, then $M[G]$ also does.
\end{abstract}
\keywords{
Isabelle/ZF, forcing, preorder, Rasiowa-Sikorski lemma, names, generic extension.
}

@@

\bibliographystyle{plain}
\bibliography{draft}
\end{document}

>>>>

\documentclass{article}
\usepackage{isabelle,isabellesym}
\usepackage{hyperref}
\usepackage[numbers]{natbib}

@@

  Given a transitive set $M$, we define its generic extension $M[G]$,
  the canonical names for elements of $M$, and finally show that if $M$
  satisfies the axiom of pairing, then $M[G]$ also does.
\end{abstract}
\keywords{
Isabelle/ZF, forcing, preorder, Rasiowa-Sikorski lemma, names, generic extension.
}

@@

\bibliographystyle{mi-estilo-else}
\bibliography{draft}
%\input{first_steps_into_forcing.bbl}
\end{document}
